What do incoming university students believe about open science practices in

### 2021-01-12 analysis/Manuscript.Rmd
Removing a comment

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```
<!--Intro below is very rough, just making sure everything works here in markdown really.-->

>>>>

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```
